\documentclass{article}
\begin{document}

\section*{Pixie}

Pixies are tiny humanoids native to the Feywild, wielding magic and brewing potions to keep themselves hidden from the outside world. They are slow to trust others but once friendship is acquired their trust is complete.
Pixies are feminine in appearance, both male and female are quite slender. Their wings are similar butterfly's and the males do not grow and bodily hair. Pixies have a light blue to olive skin coloring and hair of deep red, dark blue, pink or brown. Eyes are green, dark blue or hazel.

\subsection*{Traits}

\begin{description}
\item [Ability Score Increase] Your Dexterity score increases by 2. Your wisdom score increases by 1. Your strength score is decreased by 4, to a minimum of 2.
\item [Size] Pixies are up to 1 ft tall with slender builds. Your size is tiny.
\item [Speed] Your base walking speed is 10 feet. You have a flying speed of 30 feet and you can hover no more than 10 feet off the ground. If you are more than 10 feet off the ground when you end your turn you will fall until you are within the 10 feet of the ground.
\item [Luminous] While flying, you glow with the soft light, similar in intensity to candlelight. Because you glow, you suffer disadvantage on Stealth checks based on sight. In addition, this illuminates dark areas with your unique color - 10 ft of bright light and 10 ft of dim light beyond that.
\item [Age] Faeries do not track age the same way that other humanoid races do. A faerie doesn't mature and will never die of old age, though there exists lore that speaks of faeries dying through boredom or oppressive banality.
\item [Alignment] Faerie tend to be free-minded and they value freedom and free-will. They tend to be more chaotic, taunting strangers lost in the woods before leading them to safety and pulling jokes on unsuspecting adventurers, though these are mostly harmless. They also tend to be light hearted and of good intentions.
\item [Fey] You have advantage on saving throws against being charmed but disadvantage on saving throws against being frightened and magic can’t put you to sleep.
\item [Fey invisibility] As a bonus action you become invisible for 3 minutes or until you dismiss the invisibility as a bonus action or by attacking /casting a spell. Any equipment you are wearing or carrying is invisible with you. You must complete a long rest before using the ability again.
\item [Faerie Weaponry] Faeries can only wear weapons and armor sized for them, Tiny Weapons use damage dice 1 step lower than weapons sized for Medium characters (i.e. d8 becomes d6) to a minimum of 1 damage. Tiny Ranged Weapons have 1/2 the range of their Medium sized counterparts Items sized for tiny characters weigh 1/10 their standard weight
\item [Size Advantage] You can move through a hostile creature's space if the creature is at least two sizes larger than you, and you can share a square with a single friendly creature without crowding one another (but if you are in the same square as an ally Rogue, you do not grant Sneak Attack to the Rogue while in the same square). When sharing a square with a friendly creature or when there is another creature between you and an attacking enemy, you have half cover.
\item [Shrink] You can cast spell Enlarge/Reduce, requiring no components. When you cast the spell Enlarge/reduce it must be cast in this way:
\begin{itemize}
\item The spell can only be cast on an object. The spell is in effect until the object is in a 15ft radius around you.
\item The spell can only be used to Reduce but reduces the target to the appropriate size for a Pixie.
\item You cannot make yourself or a creature the target of the spell.
\item If the object is a weapon the trait Faerie weaponry is in effect.
\end{itemize}
\item [Forest dweller] While you're in a forest terrain, you have advantage on animal handling, nature, survival and perception checks.
\item [Languages] You can speak, read and write Common and Sylvan.
\end{description}

\end{document}